Tutorial_2

### 2024-09-17 Tutorial_2_Bayesian/Tutorial_2.Rmd
add eval=F

```{r save-plot-priors}
ggsave("Tutorial_2_Bayesian/figures/plot_of_priors.png", width=14, height=13,dpi=300)
```

@@

```{r fit-model-M1}
plan(multicore)

@@

```{r fit-model-M2}
plan(multicore)

@@

```{r fit-model-M3}
plan(multicore)

@@

```{r fit-model-M4}
plan(multicore)

@@

```{r check-model-M4}
summary(model_M4)

fixef(model_M4)[c("conditioncongruent", "conditionincongruent"), -2] %>% exp()

# the formula above comes down to the following effects:
# cloglog[h(t)]=Intercept+     ## the estimated cloglog[h(t)] in bin 9 for trial 1000 for reference condition "blank"
# period_9+I(period_9^2)+I(period_9^3)+    ##a cubic specification of TIME for reference condition "blank"
# congruent+congruent:period_9+congruent:I(period_9^2)+congruent:I(period_9^3)+      ##effect of congruent interacts cubicly with TIME
# incongruent+incongruent:period_9+incongruent:I(period_9^2)+incongruent:I(period_9^3)+     ##effect of incongruent interacts cubicly with TIME
# trial_c + trial_c:period_9 + ##linear effect of trial number in bin 9 can change linearly over TIME for "blank"
# trial_c:congruent + trial_c:incongruent + ##linear effect of trial number in bin 9 can differ for congruent and incongruent
# trial_c:congruent:period_9 + trial_c:incongruent:period_9 ##how the linear effect of trial number changes linearly over TIME can differ for congruent and incongruent
```

@@

```{r save-plot-effects}
ggsave("figures/effects_con_incon_trial1000.png", width = 12, height = 16, dpi = 600)
```

>>>>

```{r save-plot-priors, eval=F}
ggsave("Tutorial_2_Bayesian/figures/plot_of_priors.png", width=14, height=13,dpi=300)
```

@@

```{r fit-model-M1, eval=F}
plan(multicore)

@@

```{r fit-model-M2, eval=F}
plan(multicore)

@@

```{r fit-model-M3, eval=F}
plan(multicore)

@@

```{r fit-model-M4, eval=F}
plan(multicore)

@@

@@

```{r save-plot-effects, eval=F}
ggsave("figures/effects_con_incon_trial1000.png", width = 12, height = 16, dpi = 600)
```
